\documentclass{article}
\usepackage{amsmath}
\begin{document}
\title{EE 105: Devices \& Circuits}
\author{Steve Wang}
\date{\today}
\maketitle

\section*{Lab 1}
\label{sec:1}
\begin{enumerate}
\item Dangerous!
\item Diodes
  \begin{itemize}
  \item $I_D = I_S e^{V_D/V_{DD}}$
  \end{itemize}
\item (overview of lab)
\end{enumerate}

\section*{Diodes}
\label{sec:2}
[ stuff about back-to-back diodes ]

\section*{Band Theory of Semiconductors}
\label{sec:3}
Bohr, Pauli $\implies$ energy bands. From Razavi perspective, silicon
atoms each have bonds to each other. At absolute zero, all of these
things are locked in place. You can put a potential across it, and
none of the electrons can move.

If you heat this thing up, a few electrons become charge carriers and
leave behind holds. yields electric field, conduction band moves.

Electrons in conduction band are negative or n-type carriers; holes in
valence band are positive or p-type carriers.

Thermal excitation $\implies$ electron-hole pair (ehp)

In pure silicon (``intrinsic'') the number of n-type carriers ($n$)
equals the number of p-type carriers ($p$) equals the intrinsic number
($n_i$). This number is a strong function of the temperature.

\subsection*{Doping}
\label{sec:3a}
In general, we do not work with intrinsic silicon -- you intentionally
muck with the concentrations of n- and p-type carriers through a
process known as ``doping''.

If you add phosphorus or arsenic (V), they have five valence
electrons. They contribute an electron and are thus considered donors.

Boron is of group III and has three valence electrons. It generates a
hole, so it's an acceptor.

This changes the number of n- and p-type carriers in your sample. If
you dope predominantly with a donor, you make n-type material.

$N_D = \# \text{ donor atoms}/\text{cm}^3 \equiv n$. $N_A = \#
\text{ acceptor atoms}/\text{cm}^3 \equiv p$. $N_D$ and $N_A$ typically
vary from $10^{12}$ to $10^{20}$ per cubic centimeter.

PHYSICS MAJIKKS: For intrinsic, it's true that $n = p = n_i$. It's
actually always true that $np = n_i^2$, even after doping.

% [ note: 241 Cory ]

\end{document}
