\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\begin{document}
\title{EE 105: Devices \& Circuits}
\author{Steve Wang}
\date{\today}
\maketitle

\section{Stuff}
\label{sec:1}
Piazza.

Homework 1.

\subsection{Lab 1}
\label{sec:1a}
Goal: Measure voltage on wall plug. Fat blade $\implies$ ground.
\\ Don't screw up.

\section{Conduction}
\label{sec:2}
drift: electric field
\\
diffusion: nonuniform concentration gradient

n-type dopants (P, Ar)

p-type dopants (B)

intrinsic silicon (undoped): $n = p = n_i \propto T^{3/2}e^{-E_g/k_BT}$

$E_g \equiv 1.1 eV$

doped: stuff happens to control these concentrations.

If you plot concentration in \# per cubic centimeter vs Temperature,
we know that $n_i$ is $10^{10}$ at room temperature, goes up to
$10^{15}$.

Huge change in $n_i$, though. minority carriers affected more by
temperature. etc.

\subsection{Drift}
\label{sec:2a}

Drift in solids. terminal velocity, somewhat.

initially, straight line (in log-linear graph). slope called mobility
($\mu$). $v = \mu E$. Doesn't do that forever. Other things start
happening as well, and you end up getting a limit.

$\mu$ depends on collisions. higher T $\implies$ lower $\mu$. higher doping
$\implies$ lower $\mu$.

\subsection{Diffusion}
\label{sec:2b}
brownian motion, random walk, statistical mechanics, etc.

Einstein relation: $D/\mu = kT/q$

\section{PN Junction}
\label{sec:3}
Diode has two regions, N, P. Two carrier types: n, p. two types of
conduction: drift, diffusion.

Ionization from diffusion generates voltage difference, induces electric
field. Drift pushes electrons back and cancels out diffusion. This is
equilibrium, i.e. no net flow of electrons or holes.

\end{document}
